\sysfull

### 2018-04-17 paper/coalescing.tex
coalescing edits

When a device's buffered energy is sufficient to run multiple consecutive tasks
without a power failure, committing state after each task is an unnecessary
overhead.   \sys eliminates this overhead by {\em coalescing} a sequence of
consecutive tasks. \sys coalesces a sequence of tasks by deferring the commit
operations for all tasks to the end of the sequence, performing their commits
as a batch.  In general, committing involves moving state manipulated by a task
into its permanent location in non-volatile main memory.  In particular, \sys's
commit procedure copies dirty pages of memory that a task updated between fast,
volatile working memory and slower, non-volatile main memory; we defer the
details of paging and commit to Section~\ref{sec:memory_virtualization}.

@@

\noindent \textbf{Task Coalescing Strategies.} 
% % Carlo pseudo code 
% \begin{algorithm}[t]
% 	\caption{Coalescing}
% 	\label{algo:genCoalescing}
% 	\scriptsize
% 	%\small
% 	\begin{algorithmic}[1]
%         \State $H_\text{p} \gets H_\text{c}$
%         \State $H_\text{p} \gets 0$ 
%         \State $B \leftarrow $ \Call{$f_\text{reboot}$}{$B, H_\text{p}$}

@@

\begin{wrapfigure}{t}{0.3\textwidth}
\fbox{\parbox{\linewidth}{
	\captionof{algorithm}{Coalescing}
	\label{algo:genCoalescing}
	\scriptsize
	%\small
	\begin{algorithmic}[1]
        \State $B \leftarrow $ \Call{$f_\text{reboot}$}{$H$}
        \State $H \gets 0$ 
        \While{$\texttt{true}$}       
	        \State $ i \gets 0$
	        %
	        \While{$ i <= B$}
		        \State \Call{execute\_task}{$T_\texttt{i}$}
		        \State $W \leftarrow $ \Call{$f_\text{weight}$}{$T_\text{i}$}
		        \State $i \gets i + W$
				\State $H \gets H + W$
	        \EndWhile
	        %
	        \State \Call{commit\_to\_fram}{\null}
	        \State $B \leftarrow $ \Call{$f_\text{commit}$}{$B$}
        \EndWhile
	\end{algorithmic}}}
\end{wrapfigure}
%	\begin{subfigure}[t]{\linewidth}
%	\end{subfigure}
%
%
Algorithm~\ref{algo:genCoalescing} shows the general structure of a coalescing
strategy. In the algorithm, $B$ (target budget) is total number of static tasks
that \sys will next attempt to coalesce. $T_\text{i}$ is the $i^{th}$ task
executed since the last power failure. $H$ (history) is the number tasks
(coalesced or not) executed between the two most recent power failures.
$W_\text{i}$ is the {\em weight} of a task $T_\text{i}$.  A task's weight is an
arbitrary quantity associated with the task that represents its cost in time or
energy to execute; different coalescing strategies may apply different weights
to a task.  For example, a uniform weighting scheme sets the weight of each
task to one, making them all effectively equal in cost to the coalescing
algorithm.  A different policy might use a weighting scheme that sets a task's
weight equal to its run time relative to the task that executes for the
shortest duration, which has unity weight.

@@

A very simple {\em energy-oblivious} coalescing strategy treats all tasks as
having unity weight and varies the size of a coalesced task linearly. In such a
scheme, the number of tasks to coalesce, $B$, increases by a constant $x$ when
a coalesced sequence of tasks commits, and decreases by the same constant $x$
when a coalesced sequence of tasks fails to complete (i.e., after a power
failure).  The characteristic operations of the energy-oblivious strategy are:

@@

\begin{wrapfigure}{t!}{0.5\textwidth}
	\centering
	\includegraphics[width=0.5\columnwidth]{figures/slowCoal}
	\caption{The {\em energy-oblivious coalescing} algorithm \emph{linearly} updates its coalescing target.}
	\label{fig:energyBlind}
\end{wrapfigure}

@@

\subsubsection{History-Guided Coalescing (HG)}
\label{subsec:energyAware}
The History-Guided (HG) coalescing strategy adapts the coalescing target more
quickly, addressing a key limitation of the EO coalescing strategy.  
%
EA gives each task unity weight, as with EO.  
%
HG differs from EO in how it updates $B$ on commit, and after a power failure.
%
HG assumes that as the duration of execution since a power failure increases,
the amount of energy remaining decreases, and the risk of failing during a long
sequence of coalesced tasks increases.  
%
Consequently, HG decreases the coalescing target by half with each successful commit.
%
HG is {\em history-guided} because it initializes the coalescing target to be
equal to $H$, the total number of tasks executed between the most recent pair
of power failures.
%
While a history of $H$ suggests that there is sufficient energy to coalesce and
successfully commit $H$ tasks (i.e., to set $B = H$), HG conservatively sets $B$ equal to half
of $H$ moderating the risk of a very long coalesced task. 
%
The fraction of the history by which HG adjusts $B$ is arbitrary.
We experimented with a range of fraction values, settling on one half as the
default for HG, because one half had the highest performance.

@@

Figure~\ref{fig:energyAware} illustrates the operation of the history-guided
coalescing strategy.  Each white box is a task and each red box is a commit.
Time goes left to right and consecutive white boxes with no intervening commit
are coalesced tasks.  A gray box is a task interrupted by a power failure.  At
the top, the figure shows the $i^{th}$ execution period, which has a history
value of $H^{(i)} = 4$.  $B$ is initially two and decreases to one.  Once the
value of $B$ reaches one, HG is, in effect, expecting a power failure,
justifying the decrease in the coalescing target.  After the power failure, HG
first updates the history $H = H^{i+1} = 8$.  HG then uses the value of $H$ to
update $B$, setting $B$ equal to four and continuing execution.

>>>>

When a device's buffered energy is sufficient to run multiple consecutive tasks
without a power failure, committing state after each task is an unnecessary
overhead. \sys eliminates this overhead by {\em coalescing} a sequence of
consecutive tasks. \sys coalesces a sequence of tasks by deferring the commit
operations for all tasks to the end of the sequence, performing their commits
as a batch.  In general, committing involves moving state manipulated by a task
into its permanent location in non-volatile main memory.  In particular, \sys's
commit procedure copies dirty pages of memory that a task updated between fast,
volatile working memory and slower, non-volatile main memory; we defer the
details of paging and commit to Section~\ref{sec:memory_virtulaization}.

@@

% % Carlo pseudo code 
% \begin{algorithm}[t]
% 	\caption{Coalescing}
% 	\label{algo:genCoalescing}
% 	\scriptsize
% 	%\small
% 	\begin{algorithmic}[1]
%         \State $H_\text{p} \gets H_\text{c}$
%         \State $H_\text{p} \gets 0$ 
%         \State $B \leftarrow $ \Call{$f_\text{reboot}$}{$B, H_\text{p}$}

@@

\begin{wrapfigure}{t}{0.3\textwidth}
\fbox{\parbox{\linewidth}{
	\captionof{algorithm}{Coalescing}
	\label{algo:genCoalescing}
	\scriptsize
	%\small
	\begin{algorithmic}[1]
        \State $B \leftarrow $ \Call{$f_\text{reboot}$}{$H$}
        \State $H \gets 0$ 
        \While{$\texttt{true}$}       
	        \State $ i \gets 0$
	        %
	        \While{$ i <= B$}
		        \State \Call{execute\_task}{$T_\texttt{i}$}
		        \State $W \leftarrow $ \Call{$f_\text{weight}$}{$T_\text{i}$}
		        \State $i \gets i + W$
				\State $H \gets H + W$
	        \EndWhile
	        %
	        \State \Call{commit\_to\_fram}{\null}
	        \State $B \leftarrow $ \Call{$f_\text{commit}$}{$B$}
        \EndWhile
	\end{algorithmic}}}
\end{wrapfigure}
%	\begin{subfigure}[t]{\linewidth}
%	\end{subfigure}
%
%
\noindent \textbf{Task Coalescing Strategies.} Algorithm~\ref{algo:genCoalescing} shows the general structure of a coalescing strategy. In the algorithm, $B$ (target budget) is total number of static tasks
that \sys will next attempt to coalesce. $T_\text{i}$ is the $i$th task
executed since the last power failure. $H$ (history) is the number tasks
(coalesced or not) executed between the two most recent power failures.
$W_\text{i}$ is the {\em weight} of a task $T_\text{i}$.  A task's weight is an
arbitrary quantity associated with the task that represents its cost in time or
energy to execute; different coalescing strategies may apply different weights
to a task.  For example, a uniform weighting scheme sets the weight of each
task to one, making them all effectively equal in cost to the coalescing
algorithm.  A different policy might use a weighting scheme that sets a task's
weight equal to its run time relative to the task that executes for the
shortest duration, which has unity weight.

@@

A very simple {\em energy-oblivious} coalescing strategy treats all tasks as
having unity weight and varies the size of a coalesced task linearly. In such a
scheme, the number of tasks to coalesce, $B$, increases by a constant $x$ when
a coalesced sequence of tasks commits, and decreases by the same constant $x$
when a coalesced sequence of tasks fails to complete, i.e., after a power
failure. The characteristic operations of the energy-oblivious strategy are:

\begin{wrapfigure}{t!}{0.3\textwidth}
	\centering
	\includegraphics[width=0.3\columnwidth]{figures/slowCoal}
	\caption{The {\em energy-oblivious coalescing} algorithm \emph{linearly} updates its coalescing target.}
	\label{fig:energyBlind}
\end{wrapfigure}

@@

@@

\subsubsection{History-Guided Coalescing (HG)}
\label{subsec:energyAware}

The History-Guided (HG) coalescing strategy adapts the coalescing target more
quickly, addressing a key limitation of the EO coalescing strategy.  
%
EA gives each task unity weight, as with EO.  
%
HG differs from EO in how it updates $B$ on commit, and after a power failure.
%
HG assumes that as the duration of execution since a power failure increases,
the amount of energy remaining decreases, and the risk of failing during a long
sequence of coalesced tasks increases.  
%
Consequently, HG decreases the coalescing target by half with each successful commit.
%
HG is {\em history-guided} because it initializes the coalescing target to be
equal to $H$, the total number of tasks executed between the most recent pair
of power failures.
%
While a history of $H$ suggests that there is sufficient energy to coalesce and
successfully commit $H$ tasks (i.e., to set $B = H$), HG conservatively sets $B$ equal to half
of $H$ moderating the risk of a very long coalesced task. 
%
The fraction of the history by which HG adjusts $B$ is arbitrary.
We experimented with a range of fraction values, settling on one half as the
default for HG, because one half had the highest performance.

@@

Figure~\ref{fig:energyAware} illustrates the operation of the history-guided
coalescing strategy.  Each white box is a task and each red box is a commit.
Time goes left to right and consecutive white boxes with no intervening commit
are coalesced tasks.  A gray box is a task interrupted by a power failure.  At
the top, the figure shows the $i$th execution period, which has a history
value of $H^{(i)} = 4$.  $B$ is initially two and decreases to one.  Once the
value of $B$ reaches one, HG is, in effect, expecting a power failure,
justifying the decrease in the coalescing target.  After the power failure, HG
first updates the history $H = H^{i+1} = 8$. HG then uses the value of $H$ to
update $B$, setting $B$ equal to four and continuing execution.
